Essay_markdown_final

### 2024-04-27 Draft_V1.Rmd
Update Draft_V1.Rmd

---
title: "Draft_markdown_v1"
author: "River Kim"
date: "2024-04-07"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

@@

```{r}
# Plotting counts of immigration texts by party
ggplot(text_count, aes(x = Year, y = n, group = party, color = party)) +
  geom_line() +
  labs(y = "Immigration texts num", x = "Year") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(format(as.Date("2007-09-14"), "%Y")), col="red") +
  annotate("text", x = as.numeric(format(as.Date("2007-09-14"), "%Y")), y = 600, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 3)

@@

```{r}
#Plotting the ratios of immigration related texts 
ggplot(filtered_ratio_count, aes(x = Year, y = ratio, group = party, color = party)) +
  geom_line() +
  labs(y = "% Immigration Texts (n>100)", x = "Year") +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0), limits = c(0, NA)) +
  scale_x_continuous(breaks = seq(min(filtered_ratio_count$Year), max(filtered_ratio_count$Year), by = 4)) +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(format(as.Date("2007-09-14"), "%Y")), col="red") +
  annotate("text", x = as.numeric(format(as.Date("2007-09-14"), "%Y")), y = 0.04, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 3)
```

@@

```{r}
# Total sentiment of text including immigration related words plot (Using negative ratio)
nrc_data %>%
  ggplot(aes(date, ratio)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", alpha=0.5) +
  labs(y = "Total NRC sentiment negative ratio", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red") +
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
```
There is no time when particularly negative emotions are revealed. Rather, negative feelings toward immigrants are less visible after the financial crisis.

@@

```{r}
# A negative sentiment ratio plot of four parties
filtered_nrc_data_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.5, size = 1) +
  geom_smooth(method="loess", se = F, alpha=0.7, size = 1) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(y = "NRC Sentiment Negative Ratio by Party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red", size = 1) +
  annotate("text", x = as.Date("2007-09-24"), y = 4, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4) +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Similar to the overall sentiment plot, there is no period when the proportion of negative words appears prominently.

@@

# Plots of specific negative sentiments by party 
long_nrc_data_neg %>%
  ggplot(aes(x = date, y = score, color = sentiment_negative)) +
  geom_smooth(method = "loess", se = F, alpha = 0.75, size = 1) +  
  geom_point(aes(shape = sentiment_negative), alpha = 0.5, size = 1) + 
  facet_wrap(~ party, scales = "free_y", nrow = 2) + 
  labs(x = "Date", y = "Score") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Regarding negative sentiments, the Conservative party presents more diverse and fluctuated points than other parties. However, the general smooth lines stay steady.
## 5) Random sample sentiment

@@

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) + 
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
  theme_minimal() +
  theme(legend.position = "bottom")
```
Negative sentiments of sample texts also show steady lines.

@@

```{r}
ggplot(selected_words, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "GloVe word embedding of words related to 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
I did it for confirming the modeling process, but we might need to use this map as a comparison plot.

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_2, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
This can be also used for comparison. Also, word embedding maps tell us the general relationships between words, especially those we are interested in.

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_4, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_1, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_2, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_3, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_1, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_2, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_4, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
We can now compare the two periods with three different embedding maps.

@@

```{r}
ggplot(df_umap_conser_pre) +
  geom_point(aes(x = Pre_Cons1, y = Pre_Cons2), color = 'blue', size = 0.05) +
  labs(title = "Conservative Party (Pre-Crisis): Word Embeddings of GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_1, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Pre-Crisis) word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_2, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Pre-Crisis) word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_3, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Pre-Crisis) word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
ggplot(df_umap_conser_post) +
  geom_point(aes(x = Post_Cons1, y = Post_Cons2), color = 'blue', size = 0.05) +
  labs(title = "Conservative Party (Post-Crisis): Word Embeddings of GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_1, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Post-Crisis) word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_2, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Post-Crisis) word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_4, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Post-Crisis) word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
ggplot(df_umap_labour_pre) +
  geom_point(aes(x = Pre_Lab1, y = Pre_Lab2), color = 'blue', size = 0.05) +
  labs(title = "Labour Party (Pre-Crisis): Word Embeddings of GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_pre_1, aes(x = Pre_Lab1, y = Pre_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Lab1, Pre_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour party (Pre-Crisis) word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_pre_2, aes(x = Pre_Lab1, y = Pre_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Lab1, Pre_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour party (Pre-Crisis) word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_pre_3, aes(x = Pre_Lab1, y = Pre_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Lab1, Pre_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour party (Pre-Crisis) word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
ggplot(df_umap_labour_post) +
  geom_point(aes(x = Post_Lab1, y = Post_Lab2), color = 'blue', size = 0.05) +
  labs(title = "Labour Party (Post-Crisis): Word Embeddings via GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_post_1, aes(x = Post_Lab1, y = Post_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Lab1, Post_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour party (Post-Crisis) word embedding of 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_post_2, aes(x = Post_Lab1, y = Post_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Lab1, Post_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour party (Post-Crisis) word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_post_3, aes(x = Post_Lab1, y = Post_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Lab1, Post_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour party (Post-Crisis) word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

>>>>

---
title: "Essay_markdown_final"
author: "River Kim"
date: "2024-04-07"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

@@

```{r}
# Plotting counts of immigration texts by party
ggplot(text_count, aes(x = Year, y = n, group = party, color = party)) +
  geom_line() +
  labs(y = "Immigration texts num", x = "Year") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(format(as.Date("2007-09-14"), "%Y")), col="red") +
  annotate("text", x = as.numeric(format(as.Date("2007-09-14"), "%Y")), y = 600, label="Northern Rock\nBailout", angle=90, color = "black", size = 3)

@@

```{r}
#Plotting the ratios of immigration related texts 
ggplot(filtered_ratio_count, aes(x = Year, y = ratio, group = party, color = party)) +
  geom_line() +
  labs(y = "% Immigration Texts (n>100)", x = "Year") +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0), limits = c(0, NA)) +
  scale_x_continuous(breaks = seq(min(filtered_ratio_count$Year), max(filtered_ratio_count$Year), by = 4)) +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(format(as.Date("2007-09-14"), "%Y")), col="red") +
  annotate("text", x = as.numeric(format(as.Date("2007-09-14"), "%Y")), y = 0.04, label="Northern Rock\nBailout", angle=90, color = "black", size = 3)
```

@@

```{r}
# Total sentiment of text including immigration related words plot (Using negative ratio)
nrc_data %>%
  ggplot(aes(date, ratio)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", alpha=0.5) +
  labs(y = "Total NRC sentiment negative ratio", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red") +
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nBailout", angle=90, color = "black", size = 4)
```
There is no time when particularly negative emotions are revealed. Rather, negative feelings toward immigrants are less visible after the financial crisis.

@@

```{r}
# A negative sentiment ratio plot of four parties
filtered_nrc_data_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.5, size = 1) +
  geom_smooth(method="loess", se = F, alpha=0.7, size = 1) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(y = "NRC Sentiment Negative Ratio by Party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red", size = 1) +
  annotate("text", x = as.Date("2007-09-24"), y = 4, label="Northern Rock\nBailout", angle=90, color = "black", size = 4) +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Similar to the overall sentiment plot, there is no period when the proportion of negative words appears prominently.

@@

# Plots of specific negative sentiments by party 
long_nrc_data_neg %>%
  ggplot(aes(x = date, y = score, color = sentiment_negative)) +
  geom_smooth(method = "loess", se = F, alpha = 0.75, size = 1) +  
  geom_point(aes(shape = sentiment_negative), alpha = 0.5, size = 1) + 
  facet_wrap(~ party, scales = "free_y", nrow = 2) + 
  labs(x = "Date", y = "Score") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Regarding negative sentiments, the Conservative party presents more diverse and fluctuated points than other parties. However, the general smooth lines stay steady.

## 5) Random sample sentiment

@@

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) + 
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nBailout", angle=90, color = "black", size = 4)
  theme_minimal() +
  theme(legend.position = "bottom")
```
Negative sentiments of sample texts also show steady lines.

@@

```{r}
ggplot(selected_words, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total speech - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
I did it for confirming the modeling process, but we might need to use this map as a comparison plot.

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_2, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total speech - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
This can be also used for comparison. Also, word embedding maps tell us the general relationships between words, especially those we are interested in.

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_4, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total speech - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_1, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total speech - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_2, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total speech - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_3, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total speech - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_1, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total speech - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_2, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total speech - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_4, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total speech - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
We can now compare the two periods with three different embedding maps.

@@

```{r}
ggplot(df_umap_conser_pre) +
  geom_point(aes(x = Pre_Cons1, y = Pre_Cons2), color = 'blue', size = 0.05) +
  labs(title = "Conservative (Pre-Crisis): Word Embeddings of GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_1, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative (Pre-Crisis) - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_2, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative (Pre-Crisis) - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_3, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative (Pre-Crisis) - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
ggplot(df_umap_conser_post) +
  geom_point(aes(x = Post_Cons1, y = Post_Cons2), color = 'blue', size = 0.05) +
  labs(title = "Conservative (Post-Crisis): Word Embeddings of GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_1, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative (Post-Crisis) - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_2, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative (Post-Crisis) - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_4, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative (Post-Crisis) - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
ggplot(df_umap_labour_pre) +
  geom_point(aes(x = Pre_Lab1, y = Pre_Lab2), color = 'blue', size = 0.05) +
  labs(title = "Labour (Pre-Crisis): Word Embeddings of GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_pre_1, aes(x = Pre_Lab1, y = Pre_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Lab1, Pre_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour (Pre-Crisis) - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_pre_2, aes(x = Pre_Lab1, y = Pre_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Lab1, Pre_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour (Pre-Crisis) - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_pre_3, aes(x = Pre_Lab1, y = Pre_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Lab1, Pre_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour (Pre-Crisis) - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
ggplot(df_umap_labour_post) +
  geom_point(aes(x = Post_Lab1, y = Post_Lab2), color = 'blue', size = 0.05) +
  labs(title = "Labour (Post-Crisis): Word Embeddings via GloVe and UMAP") +
  theme_minimal()
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_post_1, aes(x = Post_Lab1, y = Post_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Lab1, Post_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour (Post-Crisis) - 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_post_2, aes(x = Post_Lab1, y = Post_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Lab1, Post_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour (Post-Crisis) - 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_labour_post_3, aes(x = Post_Lab1, y = Post_Lab2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Lab1, Post_Lab2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Labour (Post-Crisis) - 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
